Comparing \pkg{binsegRcpp} with other implementations of binary segmentation for change-point detection

### 2025-05-07 figure-heap-refs-binsegRcpp.tex
N^1.4

% Created by tikzDevice version 0.12.6 on 2025-05-06 22:53:29
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03,150.65) --
	( 65.91,144.09) --
	( 76.80,144.10) --
	( 87.68,144.24) --
	( 98.56,144.99) --
	(109.45,146.15) --
	(120.33,147.32) --
	(131.22,148.90) --
	(142.10,150.82) --
	(152.99,152.98) --
	(163.87,155.27) --
	(174.76,157.64) --
	(185.64,160.05) --
	(196.52,162.48) --
	(207.41,164.93) --
	(218.29,167.38);
\definecolor{drawColor}{RGB}{238,130,238}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 45.09) --
	(226.46, 45.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 68.35) --
	(226.46, 68.35);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 91.60) --
	(226.46, 91.60);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 56.72) --
	(226.46, 56.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 79.97) --
	(226.46, 79.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,103.23) --
	(226.46,103.23);

@@

\path[fill=fillColor,fill opacity=0.50] ( 55.03, 60.40) --
	( 65.91, 60.67) --
	( 76.80, 60.43) --
	( 87.68, 60.60) --
	( 98.56, 60.76) --
	(109.45, 59.50) --
	(120.33, 66.90) --
	(131.22, 57.88) --
	(142.10, 60.23) --
	(152.99, 64.81) --
	(163.87, 70.91) --
	(174.76, 76.91) --
	(185.64, 83.30) --
	(196.52, 91.03) --
	(207.41, 98.65) --
	(218.29,107.54) --
	(218.29,106.55) --
	(207.41, 98.54) --
	(196.52, 90.85) --
	(185.64, 82.89) --
	(174.76, 76.69) --
	(163.87, 70.67) --
	(152.99, 64.48) --
	(142.10, 58.99) --
	(131.22, 56.22) --
	(120.33, 55.43) --
	(109.45, 56.30) --
	( 98.56, 58.85) --
	( 87.68, 58.94) --
	( 76.80, 59.07) --
	( 65.91, 58.74) --
	( 55.03, 58.77) --
	cycle;

\path[] ( 55.03, 60.40) --
	( 65.91, 60.67) --
	( 76.80, 60.43) --
	( 87.68, 60.60) --
	( 98.56, 60.76) --
	(109.45, 59.50) --
	(120.33, 66.90) --
	(131.22, 57.88) --
	(142.10, 60.23) --
	(152.99, 64.81) --
	(163.87, 70.91) --
	(174.76, 76.91) --
	(185.64, 83.30) --
	(196.52, 91.03) --
	(207.41, 98.65) --
	(218.29,107.54);

\path[] (218.29,106.55) --
	(207.41, 98.54) --
	(196.52, 90.85) --
	(185.64, 82.89) --
	(174.76, 76.69) --
	(163.87, 70.67) --
	(152.99, 64.48) --
	(142.10, 58.99) --
	(131.22, 56.22) --
	(120.33, 55.43) --
	(109.45, 56.30) --
	( 98.56, 58.85) --
	( 87.68, 58.94) --
	( 76.80, 59.07) --
	( 65.91, 58.74) --
	( 55.03, 58.77);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03, 59.02) --
	( 65.91, 59.16) --
	( 76.80, 59.39) --
	( 87.68, 59.17) --
	( 98.56, 59.18) --
	(109.45, 57.11) --
	(120.33, 56.13) --
	(131.22, 56.68) --
	(142.10, 59.59) --
	(152.99, 64.67) --
	(163.87, 70.76) --
	(174.76, 76.78) --
	(185.64, 83.14) --
	(196.52, 90.91) --
	(207.41, 98.58) --
	(218.29,106.64);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 87.68, 58.45) --
	( 98.56, 62.87) --
	(109.45, 67.15) --
	(120.33, 71.33) --
	(131.22, 75.42) --
	(142.10, 79.46) --
	(152.99, 83.44) --
	(163.87, 87.38) --
	(174.76, 91.28) --
	(185.64, 95.16) --
	(196.52, 99.01) --
	(207.41,102.83) --
	(218.29,106.64);

\path[draw=drawColor,line width= 1.1pt,line join=round] (152.99, 64.63) --
	(163.87, 71.63) --
	(174.76, 78.64) --
	(185.64, 85.64) --
	(196.52, 92.64) --
	(207.41, 99.64) --
	(218.29,106.64);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 69.01, 55.61) --
	( 87.68, 58.45) --
	(106.35, 55.61) --
	(106.35, 44.80) --
	( 69.01, 44.80) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.76, 55.61) --
	(152.99, 64.63) --
	(161.21, 55.61) --
	(161.21, 46.74) --
	(144.76, 46.74) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 87.68, 47.30) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (152.99, 47.30) {$N^2$};
\end{scope}
\begin{scope}
\path[clip] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{fillColor}{gray}{0.92}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 45.09) --
	(411.55, 45.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 68.35) --
	(411.55, 68.35);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 91.60) --
	(411.55, 91.60);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 56.72) --
	(411.55, 56.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 79.97) --
	(411.55, 79.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,103.23) --
	(411.55,103.23);

@@

\path[fill=fillColor,fill opacity=0.50] (240.12, 64.16) --
	(247.89, 60.85) --
	(255.67, 59.78) --
	(263.44, 69.26) --
	(271.22, 59.63) --
	(278.99, 57.31) --
	(286.77, 56.13) --
	(294.54, 57.00) --
	(302.32, 57.15) --
	(310.09, 59.83) --
	(317.87, 68.12) --
	(325.64, 69.02) --
	(333.41, 67.60) --
	(341.19, 71.94) --
	(348.96, 75.31) --
	(356.74, 78.25) --
	(364.51, 84.54) --
	(372.29, 85.40) --
	(380.06, 88.92) --
	(387.84, 93.02) --
	(395.61, 96.74) --
	(403.39,100.73) --
	(403.39,100.39) --
	(395.61, 96.28) --
	(387.84, 92.69) --
	(380.06, 88.71) --
	(372.29, 85.21) --
	(364.51, 81.29) --
	(356.74, 77.87) --
	(348.96, 74.21) --
	(341.19, 71.44) --
	(333.41, 67.10) --
	(325.64, 63.68) --
	(317.87, 61.35) --
	(310.09, 58.41) --
	(302.32, 56.50) --
	(294.54, 55.57) --
	(286.77, 54.88) --
	(278.99, 56.47) --
	(271.22, 58.80) --
	(263.44, 58.90) --
	(255.67, 58.75) --
	(247.89, 58.63) --
	(240.12, 59.84) --
	cycle;

\path[] (240.12, 64.16) --
	(247.89, 60.85) --
	(255.67, 59.78) --
	(263.44, 69.26) --
	(271.22, 59.63) --
	(278.99, 57.31) --
	(286.77, 56.13) --
	(294.54, 57.00) --
	(302.32, 57.15) --
	(310.09, 59.83) --
	(317.87, 68.12) --
	(325.64, 69.02) --
	(333.41, 67.60) --
	(341.19, 71.94) --
	(348.96, 75.31) --
	(356.74, 78.25) --
	(364.51, 84.54) --
	(372.29, 85.40) --
	(380.06, 88.92) --
	(387.84, 93.02) --
	(395.61, 96.74) --
	(403.39,100.73);

\path[] (403.39,100.39) --
	(395.61, 96.28) --
	(387.84, 92.69) --
	(380.06, 88.71) --
	(372.29, 85.21) --
	(364.51, 81.29) --
	(356.74, 77.87) --
	(348.96, 74.21) --
	(341.19, 71.44) --
	(333.41, 67.10) --
	(325.64, 63.68) --
	(317.87, 61.35) --
	(310.09, 58.41) --
	(302.32, 56.50) --
	(294.54, 55.57) --
	(286.77, 54.88) --
	(278.99, 56.47) --
	(271.22, 58.80) --
	(263.44, 58.90) --
	(255.67, 58.75) --
	(247.89, 58.63) --
	(240.12, 59.84);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12, 61.88) --
	(247.89, 58.83) --
	(255.67, 59.02) --
	(263.44, 59.17) --
	(271.22, 59.01) --
	(278.99, 56.82) --
	(286.77, 55.32) --
	(294.54, 55.81) --
	(302.32, 56.61) --
	(310.09, 58.78) --
	(317.87, 61.71) --
	(325.64, 63.92) --
	(333.41, 67.34) --
	(341.19, 71.65) --
	(348.96, 74.51) --
	(356.74, 77.96) --
	(364.51, 81.44) --
	(372.29, 85.27) --
	(380.06, 88.86) --
	(387.84, 92.81) --
	(395.61, 96.37) --
	(403.39,100.53);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (317.87, 58.73) --
	(325.64, 62.64) --
	(333.41, 66.51) --
	(341.19, 70.36) --
	(348.96, 74.19) --
	(356.74, 78.00) --
	(364.51, 81.79) --
	(372.29, 85.56) --
	(380.06, 89.32) --
	(387.84, 93.07) --
	(395.61, 96.80) --
	(403.39,100.53);

\path[draw=drawColor,line width= 1.1pt,line join=round] (356.74, 58.52) --
	(364.51, 65.52) --
	(372.29, 72.52) --
	(380.06, 79.52) --
	(387.84, 86.52) --
	(395.61, 93.53) --
	(403.39,100.53);
\end{scope}
\begin{scope}
\path[clip] (231.96, 41.62) rectangle (411.55,110.68);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (299.19, 55.67) --
	(317.87, 58.73) --
	(336.54, 55.67) --
	(336.54, 44.86) --
	(299.19, 44.86) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (348.51, 55.67) --
	(356.74, 58.52) --
	(364.97, 55.67) --
	(364.97, 46.81) --
	(348.51, 46.81) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (317.87, 47.36) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (356.74, 47.36) {$N^2$};
\end{scope}
\begin{scope}
\path[clip] ( 46.86,185.23) rectangle (226.46,211.31);
\definecolor{fillColor}{gray}{0.85}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 53.69) {1e-03};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 76.94) {1e-01};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91,100.20) {1e+01};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 56.72) --
	( 46.86, 56.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 79.97) --
	( 46.86, 79.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11,103.23) --
	( 46.86,103.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.6 on 2025-05-07 07:42:32
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03,144.09) --
	( 65.91,144.09) --
	( 76.80,144.10) --
	( 87.68,144.24) --
	( 98.56,144.99) --
	(109.45,146.15) --
	(120.33,147.32) --
	(131.22,148.90) --
	(142.10,150.82) --
	(152.99,152.98) --
	(163.87,155.27) --
	(174.76,157.64) --
	(185.64,160.05) --
	(196.52,162.48) --
	(207.41,164.93) --
	(218.29,167.38);
\definecolor{drawColor}{RGB}{238,130,238}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 48.78) --
	(226.46, 48.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 70.29) --
	(226.46, 70.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 91.80) --
	(226.46, 91.80);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 59.54) --
	(226.46, 59.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 81.05) --
	(226.46, 81.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,102.56) --
	(226.46,102.56);

@@

\path[fill=fillColor,fill opacity=0.50] ( 55.03, 60.60) --
	( 65.91, 61.69) --
	( 76.80, 58.47) --
	( 87.68, 58.55) --
	( 98.56, 59.43) --
	(109.45, 59.33) --
	(120.33, 60.10) --
	(131.22, 61.82) --
	(142.10, 64.29) --
	(152.99, 67.15) --
	(163.87, 73.58) --
	(174.76, 79.78) --
	(185.64, 84.15) --
	(196.52, 93.41) --
	(207.41, 99.34) --
	(218.29,107.54) --
	(218.29,106.75) --
	(207.41, 99.27) --
	(196.52, 93.30) --
	(185.64, 84.11) --
	(174.76, 79.60) --
	(163.87, 72.14) --
	(152.99, 66.65) --
	(142.10, 62.14) --
	(131.22, 61.06) --
	(120.33, 58.46) --
	(109.45, 57.76) --
	( 98.56, 57.98) --
	( 87.68, 57.21) --
	( 76.80, 57.18) --
	( 65.91, 57.79) --
	( 55.03, 57.45) --
	cycle;

\path[] ( 55.03, 60.60) --
	( 65.91, 61.69) --
	( 76.80, 58.47) --
	( 87.68, 58.55) --
	( 98.56, 59.43) --
	(109.45, 59.33) --
	(120.33, 60.10) --
	(131.22, 61.82) --
	(142.10, 64.29) --
	(152.99, 67.15) --
	(163.87, 73.58) --
	(174.76, 79.78) --
	(185.64, 84.15) --
	(196.52, 93.41) --
	(207.41, 99.34) --
	(218.29,107.54);

\path[] (218.29,106.75) --
	(207.41, 99.27) --
	(196.52, 93.30) --
	(185.64, 84.11) --
	(174.76, 79.60) --
	(163.87, 72.14) --
	(152.99, 66.65) --
	(142.10, 62.14) --
	(131.22, 61.06) --
	(120.33, 58.46) --
	(109.45, 57.76) --
	( 98.56, 57.98) --
	( 87.68, 57.21) --
	( 76.80, 57.18) --
	( 65.91, 57.79) --
	( 55.03, 57.45);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03, 60.14) --
	( 65.91, 58.16) --
	( 76.80, 57.45) --
	( 87.68, 57.47) --
	( 98.56, 58.51) --
	(109.45, 58.09) --
	(120.33, 59.09) --
	(131.22, 61.38) --
	(142.10, 63.34) --
	(152.99, 66.94) --
	(163.87, 72.43) --
	(174.76, 79.66) --
	(185.64, 84.13) --
	(196.52, 93.39) --
	(207.41, 99.29) --
	(218.29,107.49);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 76.80, 58.64) --
	( 87.68, 62.92) --
	( 98.56, 67.01) --
	(109.45, 70.97) --
	(120.33, 74.83) --
	(131.22, 78.62) --
	(142.10, 82.35) --
	(152.99, 86.03) --
	(163.87, 89.68) --
	(174.76, 93.29) --
	(185.64, 96.87) --
	(196.52,100.43) --
	(207.41,103.97) --
	(218.29,107.49);

\path[draw=drawColor,line width= 1.1pt,line join=round] (142.10, 62.16) --
	(152.99, 68.64) --
	(163.87, 75.11) --
	(174.76, 81.59) --
	(185.64, 88.06) --
	(196.52, 94.54) --
	(207.41,101.02) --
	(218.29,107.49);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 41.62) rectangle (226.46,110.68);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.12, 55.80) --
	( 76.80, 58.64) --
	( 95.47, 55.80) --
	( 95.47, 44.99) --
	( 58.12, 44.99) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.87, 55.80) --
	(142.10, 62.16) --
	(150.33, 55.80) --
	(150.33, 46.93) --
	(133.87, 46.93) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 76.80, 47.49) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.10, 47.49) {$N^2$};
\end{scope}
\begin{scope}
\path[clip] (231.96,116.18) rectangle (411.55,185.23);
\definecolor{fillColor}{gray}{0.92}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 48.78) --
	(411.55, 48.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 70.29) --
	(411.55, 70.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 91.80) --
	(411.55, 91.80);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 59.54) --
	(411.55, 59.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 81.05) --
	(411.55, 81.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,102.56) --
	(411.55,102.56);

@@

\path[fill=fillColor,fill opacity=0.50] (240.12, 58.27) --
	(247.89, 58.20) --
	(255.67, 57.82) --
	(263.44, 73.31) --
	(271.22, 58.78) --
	(278.99, 58.24) --
	(286.77, 59.39) --
	(294.54, 61.03) --
	(302.32, 60.46) --
	(310.09, 62.27) --
	(317.87, 64.16) --
	(325.64, 74.97) --
	(333.41, 69.26) --
	(341.19, 78.78) --
	(348.96, 76.56) --
	(356.74, 79.86) --
	(364.51, 82.84) --
	(372.29, 85.90) --
	(380.06, 89.36) --
	(387.84, 93.13) --
	(395.61, 96.28) --
	(403.39,100.05) --
	(403.39, 99.70) --
	(395.61, 96.10) --
	(387.84, 92.95) --
	(380.06, 89.10) --
	(372.29, 85.75) --
	(364.51, 82.37) --
	(356.74, 79.13) --
	(348.96, 75.93) --
	(341.19, 73.00) --
	(333.41, 69.00) --
	(325.64, 66.39) --
	(317.87, 63.54) --
	(310.09, 61.16) --
	(302.32, 59.96) --
	(294.54, 58.76) --
	(286.77, 58.17) --
	(278.99, 57.49) --
	(271.22, 57.71) --
	(263.44, 57.10) --
	(255.67, 57.13) --
	(247.89, 57.13) --
	(240.12, 57.43) --
	cycle;

\path[] (240.12, 58.27) --
	(247.89, 58.20) --
	(255.67, 57.82) --
	(263.44, 73.31) --
	(271.22, 58.78) --
	(278.99, 58.24) --
	(286.77, 59.39) --
	(294.54, 61.03) --
	(302.32, 60.46) --
	(310.09, 62.27) --
	(317.87, 64.16) --
	(325.64, 74.97) --
	(333.41, 69.26) --
	(341.19, 78.78) --
	(348.96, 76.56) --
	(356.74, 79.86) --
	(364.51, 82.84) --
	(372.29, 85.90) --
	(380.06, 89.36) --
	(387.84, 93.13) --
	(395.61, 96.28) --
	(403.39,100.05);

\path[] (403.39, 99.70) --
	(395.61, 96.10) --
	(387.84, 92.95) --
	(380.06, 89.10) --
	(372.29, 85.75) --
	(364.51, 82.37) --
	(356.74, 79.13) --
	(348.96, 75.93) --
	(341.19, 73.00) --
	(333.41, 69.00) --
	(325.64, 66.39) --
	(317.87, 63.54) --
	(310.09, 61.16) --
	(302.32, 59.96) --
	(294.54, 58.76) --
	(286.77, 58.17) --
	(278.99, 57.49) --
	(271.22, 57.71) --
	(263.44, 57.10) --
	(255.67, 57.13) --
	(247.89, 57.13) --
	(240.12, 57.43);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12, 57.78) --
	(247.89, 57.37) --
	(255.67, 57.22) --
	(263.44, 57.27) --
	(271.22, 57.94) --
	(278.99, 57.68) --
	(286.77, 58.62) --
	(294.54, 59.17) --
	(302.32, 60.06) --
	(310.09, 61.74) --
	(317.87, 63.77) --
	(325.64, 66.87) --
	(333.41, 69.04) --
	(341.19, 73.56) --
	(348.96, 76.03) --
	(356.74, 79.22) --
	(364.51, 82.56) --
	(372.29, 85.84) --
	(380.06, 89.21) --
	(387.84, 93.10) --
	(395.61, 96.17) --
	(403.39, 99.93);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (317.87, 61.28) --
	(325.64, 64.89) --
	(333.41, 68.47) --
	(341.19, 72.03) --
	(348.96, 75.57) --
	(356.74, 79.09) --
	(364.51, 82.60) --
	(372.29, 86.09) --
	(380.06, 89.56) --
	(387.84, 93.03) --
	(395.61, 96.48) --
	(403.39, 99.93);

\path[draw=drawColor,line width= 1.1pt,line join=round] (356.74, 61.08) --
	(364.51, 67.55) --
	(372.29, 74.03) --
	(380.06, 80.50) --
	(387.84, 86.98) --
	(395.61, 93.45) --
	(403.39, 99.93);
\end{scope}
\begin{scope}
\path[clip] (231.96, 41.62) rectangle (411.55,110.68);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (299.19, 58.23) --
	(317.87, 61.28) --
	(336.54, 58.23) --
	(336.54, 47.42) --
	(299.19, 47.42) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (348.51, 58.23) --
	(356.74, 61.08) --
	(364.97, 58.23) --
	(364.97, 49.37) --
	(348.51, 49.37) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (317.87, 49.92) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (356.74, 49.92) {$N^2$};
\end{scope}
\begin{scope}
\path[clip] ( 46.86,185.23) rectangle (226.46,211.31);
\definecolor{fillColor}{gray}{0.85}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 56.51) {1e-03};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 78.02) {1e-01};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.91, 99.53) {1e+01};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 59.54) --
	( 46.86, 59.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11, 81.05) --
	( 46.86, 81.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.11,102.56) --
	( 46.86,102.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
